---
title: "linear model"
author: "JOHANNA INIGUEZ"
date: "December 4, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(tigerstats)
```

```{r}
avast=read.csv("avast.csv")
attach(avast)
```
 
##Introduction 

This data was taken from tigerstat. The data set contains observation from job applicants  on their SIM score are strenght, grip and rating. We write these models as : 

1.SIMS = f(ARMS)       
2.SIMS = f(GRIP)       
3.SIMS = f(GRIP,ARM)      



## first model  


```{r}
model1=lm(SIMS~ARM)
summary.lm(model1)
```

The summary states the SIMS equation and shows that if and when put in the scatterplot, it creates a straight line through the points on a the plot.    





```{r}
plot(ARM,SIMS)
abline(model1)
```

The scatterplot shows that the SIMS = -.409 + 0.05 = ARMS. This equation is a straight line thoouigh the points on the  scatterplot. 



The prediction interval from model when ARMS= 88 ,GRIP 94 is :  

```{r}
newdata= data.frame (ARM=88, GRIP=94)
predict(model1,newdata,interval = "predict")
```


The first prediction value is ( fit) and the other two value are the lower and upper prediction values. 





##second model

```{r}
model2=lm(SIMS~GRIP)
summary.lm(model2)

```

The summary states the SIMS equation and shows that if and when put in the scatterplot, it creates a straight line through the points on a the plot.  



```{r}
plot(GRIP,SIMS)
abline(model1)
```


The scatterplot shows that the SIMS = -.409 + 0.05 = GRIP. This equation is a straight line thoouigh the points on the  scatterplot.   



The prediction interval from model when SIMS= 95 ,GRIP 94 is :    


```{r}
newdata= data.frame (SIMS=95, GRIP=94)
predict(model2,newdata,interval = "predict")
```


The first prediction value is ( fit) and the other two value are the lower and upper prediction values.   




## third model 


```{r}
model3=lm(SIMS~ARM+GRIP)
summary.lm(model3)
```

The summary states the SIMS equation and shows that if and when put in the scatterplot, it creates a straight line through the points on a the plot.    



```{r}
plot(SIMS~ARM+GRIP)
abline(model3)
```



The scatterplot shows that the SIMS = -.409 + 0.05 = ARM + GRIP. This equation is a straight line thoouigh the points on the  scatterplot.   


The prediction interval from model when SIMS= 95 ,GRIP 94 is ARM = 88 :       


```{r}
newdata= data.frame (SIMS=95, GRIP=94, ARM=88)
predict(model3,newdata,interval = "predict")
```

The first prediction value is ( fit) and the other two value are the lower and upper prediction values.  

```{r}
anova(model1,model3)
```

The P- value is 0.000004994 < 0.05 so we reject the null hypthesis and conclude that there is a difference between the two models. Model three is grreater since it has a smaller RSS than model 1. The null hypothesis is that there is no diffrence between model 1 and model 3. The alternative hyposthesis is that there is a differnce between the models.   
